Verifying Spatial Properties of Array Computations

### 2017-04-18 oopsla17/proofs.tex
editing checking and inference

>>>>

\closureInference*

\begin{proof}
  By \Cref{lem:vector-union}, the union of two index schemes is an
  index scheme if all components are equal except at most one
  component. Contiguity (\Cref{def:contiguity}) matches
  this precondition, thus the first part of the union in
  $\mathit{coalesce}$ produces a set of index schemes. The second part
  comprises a subset of the original index schemes.
\end{proof}
